A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-04-10 paper.Rmd
add link to the repo

In terms of lineups containing heteroskedasticity patterns, `r p_value_cmp_dat %>% filter(type == "heteroskedasticity") %>% count(conv_reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% are rejected by conventional tests, while `r p_value_cmp_dat %>% filter(type == "heteroskedasticity") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% are rejected by visual tests. The visual test rejects `r p_value_cmp_dat %>% filter(type == "heteroskedasticity") %>% filter(conv_reject == "Reject") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% of the lineups that the conventional visual test reject.

@@

The article was created with R packages `rticles` [@rticles], `knitr` [@knitr] and `rmarkdown` [@rmarkdown]. The project's Github repository (link here) contains all materials required to reproduce this article.

@@

The supplementary material is available at (link here). It includes more details about the experimental setup, the derivation of the effect size, the effect of data collection period, and the estimate of  $\alpha$.

>>>>

In terms of lineups containing heteroskedasticity patterns, `r p_value_cmp_dat %>% filter(type == "heteroskedasticity") %>% count(conv_reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% are rejected by conventional tests, while `r p_value_cmp_dat %>% filter(type == "heteroskedasticity") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% are rejected by visual tests. When the conventional test rejects a lineup, there is a good chance (`r p_value_cmp_dat %>% filter(type == "heteroskedasticity") %>% filter(conv_reject == "Reject") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`%) the visual test will also reject it.

@@

The article was created with R packages `rticles` [@rticles], `knitr` [@knitr] and `rmarkdown` [@rmarkdown]. The project's Github repository (https://github.com/TengMCing/lineup_residual_diagnostics) contains all materials required to reproduce this article.

@@

The supplementary material is available at https://github.com/TengMCing/lineup_residual_diagnostics/blob/master/appendix.pdf. It includes more details about the experimental setup, the derivation of the effect size, the effect of data collection period, and the estimate of $\alpha$.

### 2023-04-10 paper.tex
add link to the repo

In terms of lineups containing heteroskedasticity patterns, 76\% are
rejected by conventional tests, while 56\% are rejected by visual tests.
The visual test rejects 73\% of the lineups that the conventional visual
test reject.

@@

For visual tests, we expect the ``U'' shape to be detected more readily,
followed by the ``S'', ``M'' and ``triple-U'' shape. From Figure
\ref{fig:poly-power-uniform-j}, it can be observed that the power curves
mostly align with these expectations, except for the ``M'' shape, which
is as easy to be detected as the ``S'' shape. This suggests a benefit of
the visual test: knowing the shape ahead of time is \emph{not} needed
for its application.

@@

The article was created with R packages \texttt{rticles}
\citep{rticles}, \texttt{knitr} \citep{knitr} and \texttt{rmarkdown}
\citep{rmarkdown}. The project's Github repository (link here) contains
all materials required to reproduce this article.

@@

The supplementary material is available at (link here). It includes more
details about the experimental setup, the derivation of the effect size,
the effect of data collection period, and the estimate of \(\alpha\).

>>>>

In terms of lineups containing heteroskedasticity patterns, 76\% are
rejected by conventional tests, while 56\% are rejected by visual tests.
When the conventional test rejects a lineup, there is a good chance
(73\%) the visual test will also reject it.

@@

For visual tests, we expect the ``U'' shape to be detected more readily,
followed by the ``S'', ``M'' and ``triple-U'' shape. From Figure
\ref{fig:poly-power-uniform-j}, it can be observed that the power curves
mostly align with these expectations, except for the ``M'' shape, which
is as easy to be detected as the ``S'' shape. This suggests a benefit of
the visual test, the knowing the shape ahead of time is not needed for
its application.

@@

The article was created with R packages \texttt{rticles}
\citep{rticles}, \texttt{knitr} \citep{knitr} and \texttt{rmarkdown}
\citep{rmarkdown}. The project's Github repository
(\url{https://github.com/TengMCing/lineup_residual_diagnostics})
contains all materials required to reproduce this article.

@@

The supplementary material is available at
\url{https://github.com/TengMCing/lineup_residual_diagnostics/blob/master/appendix.pdf}.
It includes more details about the experimental setup, the derivation of
the effect size, the effect of data collection period, and the estimate
of \(\alpha\).
